---
title: "Test Presentation"
subtitle: "RMarkdown and Xaringan Package"
author: "Rafael Serrano-Quintero"
institute: "Department of Economics"
date: "Universitat de Barcelona"
output:
    xaringan::moon_reader:
        css: [default, metropolis, metropolis-fonts]
        lib_dir: libs
        nature:
            highlightStyle: github
            countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(hrbrthemes)
library(fontawesome)
library(knitr)
```

# Test Xaringan

## Table of Contents

1. [Introduction](#introduction)

2. [Empirical Evidence](#empirics)

3. [Model](#model)

4. [Quantitative Exercises](#quantmodel)

5. [Conclusion](#conclusions)

---
class: inverse, center, middle
name: introduction

# Introduction

<html><div style='float:left'></div><hr color = '#EB811B' size = 1px width = 796px></html>

---
# Introduction

### Me

`r fa('address-book')` [Rafael Serrano](https://sites.google.com/view/rserranoquintero)

`r fa('envelope')` [r.serrano@ua.es](mailto:r.serrano@ua.es)

`r fa('graduation-cap')` Postdoctoral Researcher (macroeconomics and growth)

### You

A quick roundtable of names, fields/interests, and coding background.

---
class: inverse, center, middle
name: empirics

# Empirical Evidence

<html><div style='float:left'></div><hr color = '#EB811B' size = 1px width = 796px></html>

---
# Data

- We present the *Star Wars Database* from `dplyr` package
- R chunk codes are shown as well
```{r}
library(dplyr)

data(starwars, package = "dplyr")

summ_tab <- starwars %>%
                filter(species == "Human") %>%
                    group_by(homeworld) %>%
                        summarise(mean_height = mean(height))
```
---
# Data

## Tables

- We can use `kable` to show nicely formatted tables

```{r}
kable(summ_tab)
```
---
# Regressions

## Regress Height on Mass

```{r}
bodymass <- lm(height ~ 1 + mass, data = starwars)
tab_coefs <- coef(summary(bodymass))

kable(tab_coefs)
```
---
# Plots

```{r}
fit <- lm(dist ~ 1 + speed, data = cars)
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = "darkgray", las = 1)
abline(fit, lwd = 2)
```
---
class: inverse, center, middle
name: model

# Model

<html><div style='float:left'></div><hr color = '#EB811B' size = 1px width = 796px></html>

---
# Main Equation

### Writing Mathematical Expressions

1. In double dollar signs `$$`
2. Write in one line, not splitted
3. Test matrices as well

$$w_i L_{di} = \beta_{di}\sum_{j\in\mathcal{N}} \omega_d^{\rho}\left(T_{ji}\kappa_{di}\right)^{1-\sigma} A_{di}^{\sigma - 1}P_{dj}^{\sigma - \rho}P_j^{\rho - 1}\nu(w_j L_j + b_j E_j)$$

$$\begin{pmatrix}
1 & 2 & 3 \\
\sigma-1 & \rho & \beta(1-\sigma)\rho \\
\sigma-\rho & 0 & 9
\end{pmatrix}$$