---
title: "Introduction to R Markdown"
author: "Rafael Serrano-Quintero"
output:
  tufte::tufte_handout: default
---

We import the necessary libraries, set the working directory, import the data, and change a bit some of the names and types of variables for further manipulation. The last line shows the first rows of the dataframe.

```{r}
# Remove everything
rm(list = ls())

# Load necessary libraries
library(readxl)
library(tidyverse)
library(dplyr)
library(epiDisplay)
library(ggplot2)

# Set working directory
user <- 1
if (user == 1) {
    setwd("D:/RESEARCH/test-languages/r-tests")
} else if (user == 2) {
    setwd(
    "C:/Users/rafse/Documents/RESEARCH/test-languages/r-tests")
} else if (user == 3) {
    setwd(
    "/home/rafserqui/Documents/Research/test-languages/r-tests")
}

fpath <- "./data/emp.xlsx"

df <- read_excel(fpath, sheet = 1, range = "A1:I1001")

df <- df %>%
    rename(emp_count = 9, gender = 2, name = 1, hwage = 8) %>%
    mutate(gender = as.factor(gender),
    emp_count = as.numeric(emp_count))

head(df)
```

Now we compute the mean, median, and standard deviation of the employment count variable.

```{r}
# Aggregate
mean(df$emp_count)
median(df$emp_count)
sd(df$emp_count)
```

What if we would like to summarize by gender and compute confidence intervals?

```{r}
# By sex
summ <- df %>%
    group_by(gender) %>%
    summarize(
        means = mean(emp_count),
        medians = median(emp_count),
        stds = sd(emp_count),
        obs = n(),
        error = qnorm(0.975) * stds / sqrt(obs),
        lb = means - error,
        ub = means + error
    )
View(summ)
```

Finally, we compute a table of frequencies and perform a $\mathcal{T}-$test for comparing means of hourly wage for men and women.

```{r}
# Table of frequencies
emp_interv <- cut(df$emp_count,
        breaks = seq(0, 6000, 500))
tab1(emp_interv, cum.percent = TRUE)

# T-Test
t.test(hwage ~ gender, data = df)
```